Turbulence in compact to giant HII regions

### 2022-02-26 strucfunc_paper.tex
Updates from Overleaf

>>>>

In the Figure~\ref{fig:strucfunc-fit-N604H}a we show the structure function of NGC 604.
The structure function present clear characteristics of periodic oscillations at large scales.
The seeing is \SI{2.2}{pc} (\(s_0\)=\SI{0.53}{\arcsecond}) and the structure function of this region lies below the true model for most of the separation range.
The correlation length is 9\(\pm\)3 pc at a \(\sigma^2\pos\) of 81\(\pm\)25 \(\text{km}^2 \text{s}^{-2}\).
A periodic pattern for the structure function appears with a maximum \(B(r)\) value of \SI{143}{km^{2}.s^{-2}} that is reached at \SI{60}{pc}, then the oscillation cause a minimum of \SI{54}{km^{2}.s^{-2}} at \SI{133}{pc} and finally it goes back up again at \SI{211}{pc} to a \(B(r)\) value of \SI{123}{km^{2}.s^{-2}}.

The EON structure function is shown in Figure~\ref{fig:strucfunc-fit-OrionLH}a.
This region presents a tapered behavior considering the inhomogeneous fluctuations of Figure~\ref{fig:model-strucfunc}b.
This observations are heavily affected by the noise which presents a value of \SI{6}{km^{2}.s^{-2}} which is larger that the \(\sigma^2\pos\) \SI{5}{km^{2}.s^{-2}}.
